Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Fixed 'top-down' not being hyphenated

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{boolean-and.pdf}
\caption{
Top down view of rendering intersecting volumes using the Boolean AND with depth
buffer masking approach.  First the part of the volume directly behind the
intersection, colored red, is rendered.  Next the intersection, colored green,
is rendered.  Then the the part of the volume directly in front of the
intersection, colored blue, is rendered.  Finally the depth buffer is masked off
using the Boolean AND so that when the cubes are rendered again, only the parts
colored yellow are rendered.
}
\label{boolean-and}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{boolean-xor.pdf}
\caption{
Top down view of rendering intersecting volumes using the Boolean AND with
Boolean XOR approach.  First the pieces behind the intersection, colored red,
are rendered.  Next the intersection, colored green, is rendered.  Then the
pieces in front of the intersection, colored blue, are rendered.  A final pass
renders the results to the screen.
}
\label{boolean-xor}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{boolean-and.pdf}
\caption{
Top-down view of rendering intersecting volumes using the Boolean AND with depth
buffer masking approach.  First the part of the volume directly behind the
intersection, colored red, is rendered.  Next the intersection, colored green,
is rendered.  Then the the part of the volume directly in front of the
intersection, colored blue, is rendered.  Finally the depth buffer is masked off
using the Boolean AND so that when the cubes are rendered again, only the parts
colored yellow are rendered.
}
\label{boolean-and}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{boolean-xor.pdf}
\caption{
Top-down view of rendering intersecting volumes using the Boolean AND with
Boolean XOR approach.  First the pieces behind the intersection, colored red,
are rendered.  Next the intersection, colored green, is rendered.  Then the
pieces in front of the intersection, colored blue, are rendered.  A final pass
renders the results to the screen.
}
\label{boolean-xor}
\end{figure}
